---
title: "Stephen Decker's CV"
author: Stephen Decker
date: "`r Sys.Date()`"
output:
  pagedown::html_resume:
    css: ['dd_cv.css', 'resume']
    # set it to true for a self-contained HTML page but it'll take longer to render
    self_contained: true
# uncomment this line to produce HTML and PDF in RStudio:
#knit: pagedown::chrome_print
---

```{r, include=FALSE}
knitr::opts_chunk$set(
  results='asis', 
  echo = FALSE
)
library(tidyverse)
library(glue)
# ======================================================================
# These variables determine how the the data is loaded and how the exports are
# done.
# Is data stored in google sheets? If no data will be gather from the csvs/
# folder in project
using_googlesheets <- TRUE
# Just the copied URL from the sheet
positions_sheet_loc <- "https://docs.google.com/spreadsheets/d/1MY5JRFv3pKLZCtqM3EmfsobBgSVt6v3PhFtv0U-JKQU/edit#gid=1730172225"
# Is this sheet available for anyone to read? If you're using a private sheet
# set this to false and go to gather_data.R and run the data loading manually
# once to cache authentication
sheet_is_publicly_readable <- TRUE
# Is the goal of this knit to build a document that is exported to PDF? If so
# set this to true to have links turned into footnotes at the end of the
# document
PDF_EXPORT <- FALSE
# A global (gasp) variable that holds all the links that were inserted for
# placement at the end
links <- c()
# ======================================================================
# Now we source two external scripts. One contains functions for building the
# text output and the other loads up our data from either googlesheets or csvs
# Functions for building sections from CSV data
source('parsing_functions.R') 
# Load data for CV/Resume
source('gather_data.R')
# Now we just need to filter down the position data to include less verbose
# categories and only the entries we have designated for the resume
position_data <- position_data %>% 
  filter(in_resume) %>% 
  mutate(
    # Build some custom sections by collapsing others
    section = case_when(
      section %in% c('research_positions', 'industry_positions') ~ 'positions', 
      section %in% c('data_science_writings', 'by_me_press') ~ 'writings',
      TRUE ~ section
    )
  ) 
```



Aside
================================================================================




Connect with Me {#contact}
--------------------------------------------------------------------------------

-   <i class="fa fa-envelope"></i> [stdecker@umass.edu](mailto:stephen.decker@hsc.utah.edu){.email}
-   <i class="fa fa-phone"></i> (713) 452-9516
-   <i class="fa fa-twitter"></i> @[decker_st](https://twitter.com/decker_st)



Links & Resources {#about}
--------------------------------------------------------------------------------
-   <i class="fa fa-file"></i> [PubMed](https://pubmed.ncbi.nlm.nih.gov/?sort=date&term=Decker+ST&cauthor_id=30471329)
-   <i class="fa-brands fa-orcid"></i> [ORCID](https://orcid.org/0000-0001-5867-1294)
-   <i class="fa fa-linkedin"></i> [LinkedIn](https://www.linkedin.com/in/deckerst/)
-   <i class="fab fa-researchgate"></i> [ResearchGate](https://www.researchgate.net/profile/Stephen-Decker-3)
-   <i class="fa fa-github"></i> [Github](https://github.com/stdecker)
-   <i class="fa fa-medium"></i> [Medium](https://medium.com/@decker_st)


Selected Skills {#skills}
--------------------------------------------------------------------------------

```{r}
build_skill_bars(professional_skills)
```

Ongoing Projects {#ongoing}
--------------------------------------------------------------------------------

*A Guide for the Analysis of High-Resolution Respirometry Data Using R*. **Version 2 Available on [GitHub](https://github.com/stdecker)**

*respirometR*: A package for analyzing Oxygraph O2K data using R. **Under development**


Disclaimer {#disclaimer}
--------------------------------------------------------------------------------

Last updated on `r Sys.Date()` using R version `r getRversion()` and [**pagedown**](https://github.com/rstudio/pagedown).






Main
================================================================================

Stephen Decker, Ph.D., ACSM-CEP {#title}
--------------------------------------------------------------------------------

### Postdoctoral Research Associate


Academic Training {data-icon=graduation-cap}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('education')
```

::: aside

**Research Philosophy**

I am extremely passionate about research and the pursuit of knowledge. 
I strongly believe that, as a researcher, it is my duty to ask rigorous 
scientific questions that test the bound of current understanding, 
and share this new knowledge in ways that enable others to have few barriers 
to new findings. In order to accomplish these goals, it is crucial to establish 
an environment that is welcoming to and accepting of individuals of all 
backgrounds and experiences, and to allow open discussion and communication 
among my scientific peers and the general public. I aim to bring an open mind
and high expectations to my research, while maintaining an inclusive environment
that also encourages free scientific thought and discovery.

:::

First Author Publications {data-icon=file}
--------------------------------------------------------------------------------


```{r}
position_data$description_1 <- stringr::str_replace(position_data$description_1, "ST Decker", "**ST Decker**")

position_data %>% print_section('first')
```


Co-Author Publications {data-icon=file}
--------------------------------------------------------------------------------

```{r}
position_data %>% print_section('pub') 
```


Manuscripts Under Review {data-icon=glasses}
--------------------------------------------------------------------------------

### Tissue-specific mitochondrial toxicity of cigarette smoke concentrate: consequence to oxidative phosphorylation

N/A

N/A

N/A

**ST Decker**, AA Matias, AE Cuadra, ME Erol, C Serviente, K Fenelon, G Layec

Under review in <i>AJP - Heart & Circ Physiol</i>



Manuscripts in Preparation {data-icon=pen}
--------------------------------------------------------------------------------

### Effects of Acute Cigarette Smoke Exposure on Simultaneous Measurements of Mitochondrial Oxygen Consumption and ROS Production <i>In Situ</i>

N/A

N/A

N/A

**ST Decker**, ST Bannon, T Huang, ME Erol, G Layec



### Effects of Sedentary Time on In Situ Mitochondrial Substrate Oxidation Across the Human Lifespan

N/A

N/A

N/A

**ST Decker**, AA Matias, ST Bannon, JP Madden, ME Erol, S Chipkin, JA Kent, MA Miller, G Layec


### Effects of Sedentary Time on In Situ Mitochondrial Substrate Oxidation Across the Human Lifespan

N/A

N/A

N/A

**ST Decker**, AA Matias, ST Bannon, JP Madden, ME Erol, S Chipkin, JA Kent, MA Miller, G Layec


### <sup>31</sup>P-MRS of Alkaline Inorganic Phosphate in Young, Sedentary Adults: A Reproducibility Study

N/A

N/A

N/A

AA Matias, ST Decker, C Serviente, ME Erol, G Giuriato, R Nagarajan, Y Le Fur, G Layec



Oral Presentations {data-icon=comment-dots}
--------------------------------------------------------------------------------


### Connecting the Dots of the Power Grid: Assessing mitochondrial membrane potential and ADP/ATP translocase activity in permeabilized skeletal muscle fiber bundles

UMass Kinesiology Seminar Series

Amherst, Massachusetts

2021



### The Physiological Role of Sirtuins: A Target for Aging or More Hype?

UMass Kinesiology Seminar Series

Amherst, Massachusetts

2019


::: aside

**Diversity Statement**

I grew up in a very diverse community, where over 300 languages and dialects were spoken and many of my childhood friends hailed from all over the world. Exposure to different peoples, traditions, and ways of thinking have been an integral part of my personal life, therefore, I value and welcome a culture that accepts people for the unique perspectives and experiences that someone may bring to my professional life. I strive to create an environment that allows all people to have an equal and safe voice in the classroom and lab and, when appropriate, allow for meaningful interactions that allow students and trainees to better understand and value others' perspectives.

:::

### Effects of Tetrahydrobiopterin on Limb Blood Flow and Muscle Metabolism in Patients with COPD

ISMRM Annual Meeting

Montreal, Quebec

2019


### Effects of High-Intensity Interval Training on Postprandial Lipemia and Glycemia

Texas ACSM

College Station, Texas

2016


### Effects of Hot and Temperate Environments on Executive Function Tasks During Moderate and Intense Exercise

SFASU Undergraduate Research Conference

Nacogdoches, Texas

2014


Selected Posters & Abstracts {data-icon=bookmark}
--------------------------------------------------------------------------------

### Oxidative Stress Induced By Long-Term Cigarette Smoke Exposure Does Not Alter Mitochondrial Respiration in Skeletal Muscle of C57BL/6 Mice

New Insights into the Biology of Exercise

Keystone, Colorado

2020

### Knockout of the Receptor for Advanced Glycation End Products (RAGE) Increases Skeletal Muscle Mitochondria Content and Alters Mitochondrial Function

Muscle Biology Conference 

Gainesville, Florida

2019


### Effects of Tetrahydrobiopterin on Limb Blood Flow and Muscle Metabolism in Patients with COPD

ACSM Annual Meeting 

Minneapolis, Minnesota

2018

### Effects of Acute Exercise on Postprandial Lipemia and Postprandial Glycemia

Texas ACSM Regional Conference

Waco, Texas

2017




Funding {data-icon=dollar-sign}
--------------------------------------------------------------------------------

### Research Travel Award Recipient

UMass Amherst Department of Kinesiology

N/A

2020

Awarded $500

### Predoctoral Fellowship

American Heart Association

N/A

2019

Not Funded

### Trainee Stipend Award

International Society for Magnetic Resonance in Medicine

N/A

2019

Awarded $200 and Conference Registration

### Student Research Development Award

Texas American College of Sports Medicine

N/A

2016

Awarded $500


Honors and Awards {data-icon=award}
--------------------------------------------------------------------------------

### Student Research Poster Finalist - Masters Category

Texas American College of Sports Medicine

Waco, Texas

2017

### Undergraduate Research Conference Top Scholar

Stephen F. Austin State University School of Honors

Nacogdoches, Texas

2014




Teaching Experience {data-icon=chalkboard-teacher}
--------------------------------------------------------------------------------


::: aside

__* Denotes Instructor of Record__




**Teaching Philosophy**

I am very enthusiastic about sharing
knowledge and teaching. I believe it
is important to acknowledge the
numerous ways in which students
learn, and how past personal
experiences shape each student’s
worldview and the learning process.
Therefore, learning must be a
journey that is tailored to students’
needs. I aim to bring an open mind
and high expectations to the
classroom, where I aspire to create
an inclusive and welcoming
environment that also encourages
students to achieve higher learning
outcomes.

:::


### KIN 272 - Anatatomy and Physiology II*

University of Massachusetts Amherst

Amherst, Massachusetts




### Kin 470 - Exercise Physiology Lab

University of Massachusetts Amherst

Amherst, Massachusetts





### KIN 270 - Anatatomy and Physiology I Lab

University of Massachusetts Amherst

Amherst, Massachusetts





### Kin 570 - Advanced Exercise Physiology

University of Massachusetts Amherst

Amherst, Massachusetts





### Kin 110 - Human Performance and Nutrition

University of Massachusetts Amherst

Amherst, Massachusetts





### Kin 100 - Physical Fitness Concepts and Activities*

Stephen F. Austin State University

Nacogdoches, Texas





### KIN 120 - Foundations of Kinesiology*

Stephen F. Austin State University

Nacogdoches, Texas





### KIN 200 - Fitness Activites for Life*

Stephen F. Austin State University

Nacogdoches, Texas





### American Red Cross CPR and Lifeguarding Instructor

Various

Texas






Professional Development & Training {data-icon=laptop}
--------------------------------------------------------------------------------

### Certified Clinical Exercise Physiologist

American College of Sports Medicine

Indianapolis, Indiana

Current

### Certified Exercise Physiologist

American College of Sports Medicine

Indianapolis, Indiana

Current

### Oroboros O2k-Workshop on High-Resolution Respirometry (HRR)

Oroboros Instruments

Schröcken, Austria

2019




Trainees {data-icon=users}
--------------------------------------------------------------------------------

### Alexs Matias (Graduate)

Trained how to collect skeletal muscle mitochondrial respiration data using the
Oxygraph O2K and the assessment of vascular function using Doppler
Ultrasound.

N/A

Present - 2019


### Enes Erol (Graduate)

Trained how to collect skeletal muscle mitochondrial respiration data using the
Oxygraph O2K and the assessment of vascular function using Doppler
Ultrasound.

N/A

Present - 2020


### Sean Bannon (Undergraduate)

**Honors Thesis:** TBD

N/A

Present - 2021

### Mia Calderone (Undergraduate)

Trained how to collect skeletal muscle mitochondrial respiration data using the Oxygraph O2K and the assessment of vascular function using Doppler Ultrasound

N/A

Present - 2020

### Jack Madden (Undergraduate)

Trained how to collect skeletal muscle mitochondrial respiration data using the Oxygraph O2K

N/A

Present - 2020

### Jyotika Vallurupalli (Undergraduate)

**Honors Thesis:** Investigating the Roles of COVID-19 on Vascular Funciton", "Trained the assessment of vascular function using Doppler Ultrasound and continuous non-invasive arterial pressure

N/A

2018 - 2021

### Sebastien Rauch (Undergraduate)

**Honors Thesis:** Validity and Specificity of Tetramethylrhodamine, Methyl Ester (TMRM) Dye in Mice Gastrocnemius Muscle Fiber Bundles for Assessing Mitochondrial Membrane Potential

N/A

2020 - 2018
